---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# excelgesis

The goal of excelgesis is to access and edit XML inside xlsx. Helper package for development and debugging of [readxl](https://github.com/hadley/readxl). Intended for personal/diagnostic use.

## Installation

You can install excelgesis from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jennybc/excelgesis")
```

## Usage

List the included examples.

```{r}
library(excelgesis)
xg_example()
```

Pick an example and store its path.

```{r}
(mg <- xg_example("mini-gap"))
```

```{r include = FALSE}
unlink("mini-gap", recursive = TRUE)
```

Unpack the xlsx, add some nice touches to make it more browser-friendly, and, if interactive, point a browser at the top-level directory.

```{r}
mg %>% 
  xg_unzip() %>% 
  xg_linkify() %>% 
  xg_browse()
```

```{r include = FALSE}
unlink("mini-gap", recursive = TRUE)
```
