---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-works_for_me-ff69b4.svg)](https://blog.codinghorror.com/the-works-on-my-machine-certification-program/)

# excelgesis

The goal of excelgesis is make the XML files inside `.xlsx` files navigable in a web browser. It's a helper package for the development and debugging of [readxl](http://readxl.tidyverse.org). excelgesis itself is intended for strictly for personal, diagnostic, and recreational use.

You can explore some prepared example workbooks here, drawn from the readxl [example](https://github.com/tidyverse/readxl/tree/master/inst/extdata) and [test](https://github.com/tidyverse/readxl/tree/master/tests/testthat/sheets) sheets:

<https://jennybc.github.io/excelgesis/>

Those same workbooks are available in `.xlsx` form in the excelgesis package. Use `xg_example()` to gain access.

The definitive reference for `.xlxs` is Standard ECMA-376 Office Open XML File Formats:

  * <http://www.ecma-international.org/publications/standards/Ecma-376.htm>

## Installation

You can install excelgesis from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jennybc/excelgesis")
```

## Usage

List the included examples.

```{r}
library(excelgesis)
xg_example()
```

Browse around the underlying XML inside those xlsx workbooks:

<https://jennybc.github.io/excelgesis/>

Here's how to do the same locally for the example workbook about Clippy:

```{r include = FALSE}
unlink("clippy", recursive = TRUE)
```

```{r}
xg_example("clippy") %>% 
  xg_inspect()
```

```{r include = FALSE}
unlink("clippy", recursive = TRUE)
```

The convenience function `xg_inspect()` wraps up three operations:

  * Unzip the ZIP archive -- `xg_unzip()`
  * Make the unpacked files more pleasant for browsing -- `xg_linkify()`
  * Visit the top-level 'index.html' in your default browser -- `xg_browse()`

Here's one last worked example using the individual functions.

```{r include = FALSE}
unlink("datasets", recursive = TRUE)
```

```{r}
(mg <- xg_example("datasets"))
mg %>% 
  xg_unzip() %>% 
  xg_linkify() %>% 
  xg_browse()
```

```{r include = FALSE}
unlink("datasets", recursive = TRUE)
```
